Three Algorithms for Merging Hierarchical Navigable Small World Graphs

### 2025-05-02 paper/main.tex
In the paper update reference to parameter L

\begin{figure}
  \centering
  \includegraphics[width=1.\linewidth]{figs/recall_vs_distance_count.pdf}
  \caption{Recall vs distance count on search stage for final merged graphs}
\label{fig:search}
\end{figure}

@@

In order to be independent of the implementation details and low level optimisation, we have done comparison of the algorithms based on the number of distance computation required for the merge process. The other important characteristics of merging process is how accurate the merge is done, i.e. how the merged graph is good for search. To quantify search quality, we performed a standard search performance test on the merged graphs. So, for the merged graphs, we have measured a trade-off between recall and the number of distance computations, by running algorithm ~\ref{alg:hnsw_search} with different values of the parameter $\ell$ (search expansion factor). We measured the recall@5 metric for $\ell$ = 32, 40, 50, 64, and 72. This metric indicates how often the true nearest neighbors appear in the top-5 results returned by the search algorithm.

@@

The searching quality of the merged graph can be seen from the Fig. ~\ref{fig:search}. The graph plots trade-off between recall and the number of distance computations. As can be seen \textsc{SIGM} with ef\_construction $\ge$ 32 and \textsc{NGM} with parameter jump\_ef = 20 produce merged graph with slightly better searing quality than other algorithms.

Another important fact which ~\ref{fig:search} shows that the number of distance computations performed by the searching algorithm (Algorithm ~\ref{alg:hnsw_search}) for equal parameter $\ell$ are almost the same.  Therefore, the graph is better if it provides better search recall for a fixed value of parameter $\ell$. Taking this into account, we can better interpret Fig. ~\ref{fig:recall_vs_merge}. It is easy to see the following:

>>>>

\begin{figure}
  \centering
  \includegraphics[width=1.\linewidth]{figs/recall_vs_distance_count.pdf}
  \caption{Recall vs distance count on search stage for merged graphs}
\label{fig:search}
\end{figure}

@@

In order to be independent of the implementation details and low level optimisation, we have done comparison of the algorithms based on the number of distance computation required for the merge process. The other important characteristics of merging process is how accurate the merge is done, i.e. how the merged graph is good for search. To quantify search quality, we performed a standard search performance test on the merged graphs. So, for the merged graphs, we have measured a trade-off between recall and the number of distance computations, by running algorithm ~\ref{alg:hnsw_search} with different values of the parameter $L$ (search expansion factor). We measured the recall@5 metric for L = 32, 40, 50, 64, and 72. This metric indicates how often the true nearest neighbors appear in the top-5 results returned by the search algorithm.

@@

The searching quality of the merged graph can be seen from the Fig. ~\ref{fig:search}. The graph plots trade-off between recall and the number of distance computations. As can be seen, \textsc{SIGM} with ef\_construction $\ge$ 32 and \textsc{NGM} with parameter jump\_ef = 20 produce merged graph with slightly better searing quality than other algorithms.

Another important fact which ~\ref{fig:search} shows that the number of distance computations performed by the searching algorithm (Algorithm ~\ref{alg:hnsw_search}) for equal parameter $L$ are almost the same.  Therefore, the graph is better if it provides better search recall for a fixed value of the parameter $L$. Taking this into account, we can better interpret Fig. ~\ref{fig:recall_vs_merge}. It is easy to see the following:
